\documentclass[12pt]{article}
\usepackage{epsfig,grffile,xspace}
\usepackage[margin=1.0in]{geometry}

\def\midterm{2}
\def\year{2022}
\def\questions{25}

\pagestyle{myheadings}
\newcommand{\myhead}{}
%% Hard to make multi-line headers, see below
% \renewcommand{\myhead}{
	% \textbf{Name:} \rule{5cm}{1pt}
	 % \hfill \textbf{Student No:} \rule{5cm}{1pt}
% } 

\newcommand{\myfoot}{\hfill Page \thepage\ \hfill}
\makeatletter
\renewcommand{\@oddhead}{\myhead}
\renewcommand{\@evenhead}{\myhead}
\renewcommand{\@oddfoot}{\myfoot}
\renewcommand{\@evenfoot}{\myfoot}
\makeatother

\begin{document}

\noindent \textbf{Name} \rule{5cm}{1pt} \hfill \textbf{Student No} \rule{5cm}{1pt}

\noindent
%% \textbf{TA} \rule{5cm}{1pt} \hfill
\textbf{Section (or time)} \rule{5cm}{1pt}

\bigskip

{\centering {\large {\bf Biology 3SS3}} \par}
{\centering Midterm \midterm, \year\par}

\parindent0pt

\vfill

This test includes {\bf \questions\ questions}. You are responsible for ensuring that your copy of the paper is complete. Bring any discrepancy to the attention of an invigilator. 

\vfill

\begin{itemize}
\item Your \textbf{version number} is shown at the top right of page 2 of your test paper: it is \textbf{important} that you fill it in on the Scan Sheet.
\item Answer all questions on the Scan Sheet. 
\item You will lose points if you don't bubble your student number and version number correctly.
\item McMaster standard calculator (Casio-FX991) is permitted for this exam.
\end{itemize}

\vfill

\textbf{Scan sheet instructions}

\small{
The scanner, which reads the sheets, senses the shaded areas by their non-reflection of light. A heavy mark must be made, completely filling the circular bubble, with an HB pencil. Marks made with a pen or felt-tip marker will \textbf{not} be sensed. Erasures must be thorough or the scanner may still sense a mark. Do \textbf{not} use correction fluid on the sheets. Do \textbf{not} put any unnecessary marks or writing on the sheet.

\begin{enumerate}
\item On side 1 (red side) of the form, in the top box, in pen, print your student number, name, course name, section number, instructor name and the date in the spaces provided. Then you {\bf MUST} sign in the space marked signature.

\item In the second box, with a pencil, mark your {\bf student number}, {\bf exam version number} and course section number in the space provided and fill in the corresponding bubbles underneath.

\item Use Red side of the form. Mark only {\bf one} choice from the alternatives (A, B, C, D, E) provided for each question. The question number is to the left of the bubbles. Make sure that the number of the question on the scan sheet is the same as the question number on the exam paper.
\item  Pay particular attention to the Marking Directions on the form.
\end{enumerate}
}

\vfill
{\centering {\large {\it Good luck!}} \par}

\end{document}
